\documentclass{iitthesis}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{amsmath}

\begin{document}

\title{Modifications to ``{\tt iitthesis.cls}''}

%~ \title{Bold math in section headings with}

%Thesis Proposal}
\author{Keith Pedersen}
\degree{}
\dept{}
\date{Feb 2018}

%\coadvisortrue           % add co-advisor. activate it by removing % symbol to add co-advisor
\maketitle

\prelimpages

\begin{acknowledgement}     % acknowledgement environment, this is optional
\par 
This acknowledgment is here so the table of contents is not mangled.
\end{acknowledgement}
% Table of Contents
\tableofcontents
\clearpage

\textpages

\Chapter{Bold math in section headings}

\Section{A section about $\sqrt{x^2+y^2}$}\label{sec:no-bold-in-text}

This section is about math. 
But notice how the math is not bolded in the section heading?
This is because \verb|\textbf| does not alter the math environment \verb|$\sqrt{x^2+y^2}$|.

\Section{A section about bolded $\boldsymbol{\sqrt{x^2+y^2}}$}\label{sec:bold-in-TOC}

I can bold the math in the section heading by using the {\tt amsmath} package 
(i.e.\ \verb|\usepackage{amsmath}|), and wrapping {\tt \verb|\boldmath|} around my math
\begin{quotation}
	\verb|\Section{A section about $\boldsymbol{\sqrt{x^2+y^2}}$}|
\end{quotation}
But notice how the math is still bolded in the table of contents (TOC)?
There is no way to tell the TOC not to use \verb|\boldmath|

\Section[Bold $\vec{a}$]{Bold $\boldsymbol{\vec{a}}$}

What we'd like is one heading for the text using \verb|\boldsymbol|, 
and one for the TOC which doesn't use \verb|\boldsymbol|.
This is what my modified \verb|\Section| command does
via its optional [bracketed] argument, 
which is how this section was declared.
Notice how the math is bolded in the sub-section heading, 
but not in the TOC? 

To use the modified \verb|\Section|, pass the heading you want 
to appear in the TOC as the optional [bracketed] argument (no \verb|\boldmath|) 
and the heading for the text as the main argument (with \verb|\boldmath|)
\begin{quotation}
	\begin{verb}
		\Section[Bold $\vec{a}$]{Bold $\boldsymbol{\vec{a}}$}
	\end{verb}
\end{quotation}
If the optional argument is not supplied
\begin{quotation}
	\begin{verb}
		\Section{A section about bolded $\boldsymbol{\sqrt{x^2+y^2}}$}
	\end{verb}
\end{quotation}
as Sections~\ref{sec:no-bold-in-text}~\&~\ref{sec:bold-in-TOC} were declared, 
then the TOC will use the main argument as the optional argument.

\Section[Careful: $e^{-x}$]{Careful: $\boldsymbol{\exp(-x)}$}

This is a manual procedure; be careful! If you change the main heading, 
you have to change the TOC heading. Notice how the TOC doesn't match this section?

\Subsection{A subsection about $\boldsymbol{y}$}
%
Subsections do not appear in the table of contents,
so we don't need an optional argument for the TOC. 
Just use \verb|\boldsymbol| for math in the heading.

\Chapter{Optional punctuation arguments for subsections and subsubsections}

\Section{The only section (to talk about subsections)}.

\Subsection{The automatic period}
% 
Periods are automatically appended to the subsection (and subsubsection) headings. 

\Subsection{Don't pass your own period.}
% 
If you pass a period in the subsection heading, you will get two.
%
\begin{quotation}
	\verb|\Subsection{Don't pass your own period.}|
\end{quotation}

\Subsection[?]{Do all subsections have to end in a period}
%
No! With my modification, an optional argument can be passed to send
some other punctuation. This optional argument defaults to a period
(i.e.\ if you want a period, you don't have to pass it).
%
\begin{quotation}
	\verb|\Subsection[?]{Do all subsections have to end in a period}|
\end{quotation}

\Subsubsection[!]{It also work for subsubsections} Huzzah!

\Subsection[;]{Be careful}
% 
you can pass any character to be use as punctuation, but not all work with the style guide.
% 
\begin{quotation}
	\verb|\Subsection[;]{Be careful}|
\end{quotation}

\end{document}
